Fluent statistical computing interfaces for biological data analysis

### 2020-10-28 Rmd/03-fluentGenomics.Rmd
add reference for MA, increase figure res

```{r workflow, fig.cap = "(ref:workflow)"}
knitr::include_graphics(here::here("img", "workflow.png"))
```

@@

The data used in this workflow is available from two packages: the **macrophage**
Bioconductor **ExperimentData** package and from the workflow package 
**fluentGenomics**.

@@

To see the results of the expression analysis, we can generate a summary table
and an MA plot:

@@

(ref:maplot) Visualization of `DESeq2` results as an "MA plot". Genes that have an adjusted *p-value* below 0.01 are colored red.

>>>>

```{r workflow, fig.cap = "(ref:workflow)"}
knitr::include_graphics(here::here("img", "workflow-fluentgenomics.pdf"))
```

@@

The data used in this workflow is available from two packages: the **macrophage**
Bioconductor **ExperimentData** package and from the workflow package 
**fluentGenomics** [@fg-pkg].

@@

To see the results of the expression analysis, we can generate a summary table and a mean-abundance (MA) plot [@Dudoit2002-vz]:

@@

(ref:maplot) Visualization of `DESeq2` results as an "MA plot". Genes  that have an adjusted *p-value* below 0.01 are colored red.In this case the LFC between conditions is shown on the y-axis, while the average normalised gene counts accross all conditions are shown on the x-axis. The assumption of an RNA-seq analysis that most genes are not DE, so most genes are scattered about zero on the y-axis while genes that have evidence of DE are far from the zero baseline. The x-axis gives a sense of the total expression of the gene.
